Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-12 manuscript/climate_sensitivity_draft.Rmd
Updated manuscript

### Introduction

Understanding how and why trees respond to drought is critical to predicting forest drought responses and climate change feedbacks. (1 paragraph on this- I have lots of content on this and will add later.)

@@

@@

Hydraulic traits were collected from SCBI and are summarized in Table 1. In August 2018, we collected leaf samples from three individuals of each species ... (**Nobby's description of methods for the following**) 
1. PLA
2. LMA
4. Wood density
5. TLP

@@

```{r, Table-cores-position, eval=TRUE, echo=FALSE, message=FALSE}

kable(table2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, traits-overview, eval=TRUE, echo=FALSE, message=FALSE}

kable(traits_table) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

@@

@@

### Results
![Table 1](tables_figures/Table1.png){width=500px}

**Table 1. Summary of hypotheses, predictions and results** 
We count predictions as fully supported (or rejected) when the direction of response matches (or contradicts) the prediction. 
H2.3-H3.2 are based on if models containing species traits in H2.1 had dAIC>=2 relative to the appropriate null model or to any alternative multivariate model within 2 dAIC. 
Parentheses indicate that predictions were partially supported (or rejected). In other words, parentheses indicate when the direction of response matched (or contradicted) the prediction in some but not all models with dAIC<2 relative to the appropriate null model. With categorical variables such as crown position,  a "(yes)" notation describes when the trend matched the prediction, but it wasn't significant 
A "(yes/no) or ("no/yes")" indicates tendencies in opposite directions in univariate tests versus the best full models, respectively. 
"(yes)
(Table 1.xlsx)

trying to test how the negative effect of height is caused by the traits,

(no) means there's a trend in the expected direction but not consistently significant

H2.3
if the effect is negative and is in every top model (<dAIC2), that would be "yes."
if the effect is negative mostly

Once the data was collected, linear mixed models were run following the order of the hypotheses as seen in Figure ??? [individual_tested_traits]. Using the [@R-pointRes] package, we set up models with the resistance value as the response variable, and each prediction's variable as the independent variable. Variables' importance in predicting drought tolerance was calculated from mixed-effects models and the lowest AICc [@R-lme4, @R-AICcmodavg].Null models were determined in order of the predictions. First, we analyzed the combined scenario to determine if "year" was significant. Upon establishing this, we tested height and DBH as size parameters. Although both were significant, height was kept due to its larger delta AICc compared with the null model. We then tested the remaining biophysical and hydraulic traits individually against a null model containing height and year. This yielded Figure ??? (cand_full). All variables with dAICc >2 were used as candidates for each scenario's best model (figure ???? (tested_traits_best))

![Table 3 (example!)](tables_figures/Table3.png)

```{r, Table 2, eval=TRUE, echo=FALSE, message=FALSE}
candidates <- read.csv("tables_figures/candidate_traits.csv")
kable(candidates, booktabs=TRUE, format = "latex", caption = "Candidate variables to be included in full model, chosen by dAICc>2 when individually tested against a null model") %>%
  kable_styling(bootstrap_options = "striped", latex_options ="hold_position")
```

```{r, Table 3, eval=TRUE, echo=FALSE, message=FALSE}
traits_best <- read.csv("tables_figures/tested_traits_best.csv")
kable(traits_best, booktabs=TRUE, format = "latex", caption = "Best full models for each drought scenario") %>%
  kable_styling(bootstrap_options = "striped", latex_options = c("scale_down", "hold_position"))
```

@@

### Supplementary Information

```{r echo=FALSE, out.width='100%', fig.cap = "Map of ForestGEO plot", fig.pos='H'}
  knitr::include_graphics("tables_figures/ForestGEO_plot.jpg")
```

@@

@@

```{r, SI Table 1, eval=TRUE, echo=FALSE, message=FALSE}
heights <- read.csv("tables_figures/height_regression.csv", stringsAsFactors = FALSE)
kable(heights, booktabs=TRUE, format = "latex", caption = "Species-specific height regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

>>>>

### Introduction
Understanding how and why trees respond to drought is critical to predicting forest drought responses and climate change feedbacks. (1 paragraph on this- I have lots of content on this and will add later.)

@@

**Table 1. Summary of hypotheses, predictions and results** 
![Table 1](tables_figures/Table1.png){width=500px}

We count predictions as fully supported (or rejected) when the direction of response matches (or contradicts) the prediction. 
H2.3-H3.2 are based on if models containing species traits in H2.1 had dAIC>=2 relative to the appropriate null model or to any alternative multivariate model within 2 dAIC. 
Parentheses indicate that predictions were partially supported (or rejected). In other words, parentheses indicate when the direction of response matched (or contradicted) the prediction in some but not all models with dAIC<2 relative to the appropriate null model. With categorical variables such as crown position,  a "(yes)" notation describes when the trend matched the prediction, but it wasn't significant 
A "(yes/no) or ("no/yes")" indicates tendencies in opposite directions in univariate tests versus the best full models, respectively. 
"(yes)

@@

Hydraulic traits were collected from SCBI and are summarized in Table 1. In August 2018, we collected leaf samples from three individuals of each species ... (**Nobby's description of methods for the following (see word document**) 
1. PLA
2. LMA
4. Wood density
5. TLP

@@

```{r, Table2, eval=TRUE, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
table2 <- read.csv("tables_figures/Table2.csv")
kable(table2, booktabs=TRUE, format = "latex", caption = "Overview of analyzed species, detailing DBH mean and range of cored trees, the number of cores represented by each crown position of each species, and mean hydraulic trait measurements. Units of measurements are in mm (DBH), % (PLA), g/m2 (LMA), MPa (TLP), and g/cm3 (WD).") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

@@

### Results
Once the data was collected, linear mixed models were run following the order of the hypotheses as seen in Figure ??? [individual_tested_traits]. Using the [@R-pointRes] package, we set up models with the resistance value as the response variable, and each prediction's variable as the independent variable. Variables' importance in predicting drought tolerance was calculated from mixed-effects models and the lowest AICc [@R-lme4, @R-AICcmodavg].Null models were determined in order of the predictions. First, we analyzed the combined scenario to determine if "year" was significant. Upon establishing this, we tested height and DBH as size parameters. Although both were significant, height was kept due to its larger delta AICc compared with the null model. We then tested the remaining biophysical and hydraulic traits individually against a null model containing height and year. This yielded Figure ??? (cand_full). All variables with dAICc >2 were used as candidates for each scenario's best model (figure ???? (tested_traits_best))

**Describe each individual drought scenario **
1964-1966
1977
1999

@@

**Results for first main question: what drives the observed tendency for large trees to suffer more during drought?**
H1.0, H1.1, H1.2, H1.3
DBH, height, crown position, and TWI

![Height profile graphs]
(tables_figures/height graphs ){width=500px}

**Results for second main question: how do species' traits - alone and in interaction with tree size - influence drought response? **
H2.1, H2.2, H2.3
Hydraulic traits alone, traits with height

![Table 3 (example!)](tables_figures/Table3.png) #this is tested_traits_all

**Results for third main question: are responses similar or variable across individual drought years?**
H3.1 and H3.2
Combining biophysical with hydraulic traits, which come out as candidates for best model?

@@

### Supplementary Information
```{r, Table S1, eval=TRUE, echo=FALSE, message=FALSE}
heights <- read.csv("tables_figures/height_regression.csv", stringsAsFactors = FALSE)
kable(heights, booktabs=TRUE, format = "latex", caption = "Species-specific height regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

@@

```{r, Table S2, eval=TRUE, echo=FALSE, message=FALSE}
tableS2 <- read.csv("tables_figures/candidate_traits.csv", stringsAsFactors = FALSE)
kable(tableS2, booktabs=TRUE, format = "latex", caption = "Candidate variables for best model") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r, Plot, echo=FALSE, out.width='100%', fig.cap = "Map of ForestGEO plot", fig.pos='ht'}
  knitr::include_graphics("tables_figures/ForestGEO_plot.jpg")
```

*how do we want to present Table S3? Would it be better as an image of an excel file, since it's so large? Did we want to keep all coefficients here?*
```{r, Table S3, eval=TRUE, echo=FALSE, message=FALSE}
tableS3 <- read.csv("tables_figures/top_models_dAIC.csv", stringsAsFactors = FALSE)
kable(tableS3, booktabs=TRUE, format = "latex", caption = "Top model variations for each drought scenario, with dAICc values <= 2") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

@@
